Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-08-27 main.tex
Fixed typo in LCAO game equation Added appendix description for IND-CPA and AO (included description of public key scheme, and aggregator oblivious scheme)

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
\section{Aggregator Obliviousness (AO)} \label{app:ao}

>>>>

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
\end{description}

The security game between attacker and challenger for IND-CPA is given by
\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public key $pk$ to the attacker
    \item[Encryptions] The attacker may compute encryptions using the public key $pk$.
    \item[Challenge] Next, the attacker chooses two values
    \begin{equation*}
        x^{(0)} \text{ and } x^{(1)}
    \end{equation*}
    and gives them to the challenger. The challenger then chooses a random bit $b \in \{1,0\}$ and returns the encryption
    \begin{equation*}
        \mathcal{E}_{pk}(x^{(b)}).
    \end{equation*}
    \item[More Encryptions] The attacker can now compute more encryptions with the public key $pk$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{IND-CPA}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

\section{Aggregator Obliviousness (AO)} \label{app:ao}
An aggregator oblivious encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{AggDec})$, defined as
\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At time $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
\end{description}

The security game between attacker and challenger for AO is given by
\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
    \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
    \begin{enumerate}
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_i)$ and $(i',t',x^{\prime(t')}_{i'}$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i} = x^{\prime(t')}_{i'}\,.
        \end{equation*}
        They are given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_i)\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_i)\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S} x^{(t^*)(0)}_i = \sum_{i \in S} x^{(t^*)(1)}_i\,.
    \end{equation*}
    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{sk_i}(x^{(t^*)(b)}_i)\,|\,i\in S\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now submit more queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{AO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}
